---
title: "Processing Results from the EIRR-ww model"
author: "Isaac H Goldstein"
date: today
format: html
editor: visual
---

## Overview

This document shows how to use `R` code to process MCMC samples from the EIRR-ww model generated in `Julia` to create dataframes used to summarise frequentist metrics and visualize results. This document combines code from `scripts/process_results/process_results_eirrc_closed.R` and `scripts/visualize_results/visualize_fit_to_LA.R`.

## Install libraries

```{# {r}
#| eval: false
install.packages(c("tidyverse", 
                    "tidybayes",
                    "posterior",
                    "fs", 
                    "GGally",
                    "gridExtra",
                    "cowplot",
                    "scales",
                    "lubridate",
                    "viridis",
                    "EpiEstim",
                    "zoo"))
```

## Load libraries, choose simulation and seed

For a list of the meanings of the possible scenarios, see `vignettes/fit_eirr_ww.qmd`. This document defaults to assuming `sim="real` and `seed=1` as in the previous vignette.

```{r}
#| output: false
library(tidyverse)
library(tidybayes)
library(posterior)
library(fs)
library(GGally)
library(gridExtra)
library(cowplot)
library(scales)
source(here::here("src/wastewater_functions.R"))
sim = "real"
seed = 1

# a hack for dealing with re-using scenario 1 data
repeat_scenario1s = c(3,4,5,6,7,8,9,10, 12, "frw")
repeat_scenario41s = c(411, 4111)

if (sim %in% repeat_scenario1s) {
  scenario_sim = 1
} else if (sim %in% repeat_scenario41s) {
  scenario_sim = 41
} else {
  scenario_sim = sim
}


```

## load posterior samples, calculate mcmc diagnostics

```{r}
gq_address <- paste0("vignettes/generated_quantities_scenario", 
                     sim, 
                     "_seed", 
                     seed,
                     ".csv")

posterior_samples <- read_csv(here::here(gq_address)) %>%
  rename(.iteration = iteration,
         .chain = chain) %>%
  as_draws()


subset_samples <- subset_draws(posterior_samples)

mcmc_summary <- summarise_draws(subset_samples)

```

## create long format mcmc samples

This code creates two dataframes: one with the mcmc samples for non-time-varying parameters, the other quantiles of the time-varying parameters.

```{r}
posterior_gq_samples_all <- subset_samples  %>%
  pivot_longer(-c(.iteration, .chain)) %>%
  select( name, value)


posterior_fixed_samples <- make_fixed_posterior_samples(posterior_gq_samples_all)

posterior_timevarying_quantiles <- make_timevarying_posterior_quantiles(posterior_gq_samples_all)

```

## create posterior predictive quantiles

This code creates quantiles for the posterior predictive for each day there was observed data

```{r}
post_pred_address <- paste0("vignettes/posterior_predictive_scenario",
                            sim,
                            "_seed",
                            seed,
                            ".csv")
eirr_post_pred <- read_csv(here::here(post_pred_address))

if (sim != "real" & sim != "uci" & sim!= "uci_region1" & sim != "uci_region2" & sim != "uci_region3") {
  if (sim != 12 & scenario_sim != 41) {
    simdata_address <- paste0("data/sim_data/scenario", scenario_sim, "_fitted_genecount_obsdata.csv")
    
    simdata <- read_csv(here::here(simdata_address)) %>%
      dplyr::filter(seed == seed)
    
  } else if (sim == 12) {
    simdata_address <- paste0("data/sim_data/scenario", scenario_sim, "_lump2data_seiirr_100sims.csv")
    
    simdata <- read_csv(here::here(simdata_address)) %>%
      dplyr::filter(seed == seed)
    
  } else if (scenario_sim == 41) {
    simdata <- read_csv(here::here("data", "sim_data", "scenario41_fitted_obsdata.csv")) 
  }

} else if (sim == "real") {
  simdata_address <- "data/LA_daily_data_feb2022.csv"

  simdata <- read_csv(here::here(simdata_address))

} else if (sim == "uci") {

  simdata <- read_csv(here::here("data", "uci_data", "uci_fitting_data.csv"))
  
} else if (sim == "uci_region1") {
  
  simdata <- read_csv(here::here("data", "uci_data", "uci_fitting_data_region1.csv"))
  
} else if (sim == "uci_region2") {
  
  simdata <- read_csv(here::here("data", "uci_data", "uci_fitting_data_region2.csv"))
  
} else if (sim == "uci_region3") {
  
  simdata <- read_csv(here::here("data", "uci_data", "uci_fitting_data_region3.csv"))
  
}

if (sim == 3) {
  ten_sim_val = TRUE
} else {
  ten_sim_val = FALSE
}

if (sim == 4) {
  three_mean_val = TRUE
} else {
  three_mean_val = FALSE
}

eirr_post_pred_intervals <- make_post_pred_intervals(eirr_post_pred, simdata, ten_sim = ten_sim_val, three_mean = three_mean_val)
```

## Visualizing the posterior of Rt

Once the time-varying quantiles have been created, we can visualize them. In this vignette, we visualize the quantiles of Rt for Los Angeles, CA.

```{r}
# first read in the data

real_data <- read_csv(here::here("data/LA_daily_data_feb2022.csv"))

# generate crosswalk between model time and actual date

real_data$epi_week[real_data$year == 2022] <- real_data$epi_week[real_data$year == 2022] + 52
date_week_crosswalk <- real_data %>% 
  dplyr::select(date, epi_week, new_time) %>%
  mutate(time = epi_week - 27)

# then we filter the time-varying quantiles dataframe for the Rt quantiles and visualize
rt_quantiles_eirr <- posterior_timevarying_quantiles %>%
  filter(name == "rt_t_values") %>%
  left_join(date_week_crosswalk, by = "time") %>%
  dplyr::select(time, date, epi_week, value, .lower, .upper, .width,.point, .interval) 

fill_date = as.Date("2021-10-11")
fill_week = 41

rt_quantiles_eirr$date[is.na(rt_quantiles_eirr$date)] <- fill_date
rt_quantiles_eirr$epi_week[is.na(rt_quantiles_eirr$epi_week)] <- fill_week
# visualize results
# all credit to Damon Bayer for plot functions 
my_theme <- list(
  scale_fill_brewer(name = "Credible Interval Width",
                    labels = ~percent(as.numeric(.))),
  guides(fill = guide_legend(reverse = TRUE)),
  theme_bw(),
  theme(legend.position = "bottom"))




eirrc_realdata_rt_plot_seed1 <- rt_quantiles_eirr %>%
  ggplot(aes(date, value, ymin = .lower, ymax = .upper)) +
  geom_lineribbon() +
  scale_y_continuous("Rt", label = comma, breaks = c(0:5), limits = c(0,5)) +
  scale_x_date(name = "Date", date_breaks = "month") +
  ggtitle("EIRR-ww Posterior Rt") +
  my_theme + 
  theme(axis.text.x = element_text(angle = 90),
        legend.position = c(0.4, 0.75),
        text = element_text(size = 18),
        legend.background = element_blank())


eirrc_realdata_rt_plot_seed1

```
